To Do List

### 2018-09-19 ToDo.Rmd
updates

* Finish TFBS models
* Include column for feature table for why a feature was excluded
* Use tables instead of barplots for performance metrics
* class imbalance barplot unnecessary, put in words
* clean up class imbalance plot put bar underneath to categorize each technique; put x axis diagonally
* put tad in boundary before tad not in boundary for class imbalance table
* include venn diagram of selected features
* create a heat map for AIC values from commonly selected features
* look at chromosome specific models and compare
* look at different resolutions (talk with john)
* look at other type of transformation (inverse sine transformation)

>>>>

* Finish TFBS models
+ Include column for feature table for why a feature was excluded
+ Use tables instead of barplots for performance metrics
+ class imbalance barplot unnecessary, put in words
* clean up class imbalance plot put bar underneath to categorize each technique; put x axis diagonally
* put tad in boundary before tad not in boundary for class imbalance table
* include venn diagram of selected features
* create a heat map for AIC values from commonly selected features
+ look at chromosome specific models and compare
* look at different resolutions (talk with john)
+ look at other type of transformation (inverse sine transformation)
